---
title: "Reproducible Research: Peer Assessment 1"
author: "dar7yl"
date: "Monday, February 09, 2015"
output: html_document
keep_md: true
---
### Project Instructions
* [Project Instructions on website](https://class.coursera.org/repdata-011/human_grading/view/courses/973512/assessments/3/submissions)
* [local Copy](RepData_PeerAssessment1/doc/instructions.pdf)

## Loading and preprocessing the data
The data is from a personal activity monitoring device that collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

* The data for this assignment can be downloaded from the course web site:
		[Activity monitoring data ](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip) - 52K
```{r load_data, echo=TRUE}

load_data <- function()
{
	library(downloader)
	
	fileurl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
	zipfile <- file.path("data", "repdata_data_activity.zip")
	
	print(paste("Downloading files from '",fileurl,"' to '",zipfile,"'",sep="") )
	
	download.file(fileurl, zipfile, quiet = FALSE, mode = "wb", cacheOK = TRUE )

	print("Unzipping")
	unzip(zipfile, junkpaths=TRUE, exdir="data", unzip="internal", setTimes=FALSE)
	print(paste("file is now in", zipfile), sep=" ")

	#we'll go right ahead and read the data and put it in the global environment
	activity_Classes <- c( "numeric", "Date", "numeric")

	activity <- read.csv(zipfile, colClasses= activity_Classes)
	assign("activity", activity, envir = .GlobalEnv,) 
}
	
```
## What is mean total number of steps taken per day?

## What is the average daily activity pattern?
```{r means, echo=TRUE, eval=TRUE}

means<-aggregate( activity$steps, by=list(activity$date), 
						FUN=mean, na.action = na.omit)
summary(means)
tmean<-mean(means$x, na.rm=TRUE)
tmean
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
